Unbiased pangenome graphs

### 2022-08-08 manuscript/main.tex
Replace `\mathcal{P}` with `|P|`; specify that we refer to the size of the array; add missing backslash

Considering the time complexity of induction, we anticipate $O(|A|\log|A|)$ time to sort the match set and $O(\mathcal{N} \log |A|)$ to query it and compute our $\mathcal{N}$ transitive closures.
Computing the variation graph paths $\mathcal{P}$ involves converting sequences in $S$ to walks through $\mathcal{N}$.
We first sort the sequence-to-graph mapping array $Z$ in $O(\mathcal{Q} \log \mathcal{Q})$ operations, and then compute $\mathcal{P}$ in $O(\mathcal{Q})$ queries which each cost $O(\log \mathcal{Q})$.
To obtain unique edges and generate $\mathcal{E}$, we must build and sort an array of $O(2\mathcal{P})$, and then iterate through it for $O(2\mathcal{P} \log 2\mathcal{P} + 2\mathcal{P})$ operations.
In sum, we would expect to require $O(|A|\log|A| + \mathcal{N} \log |A| + 2(\mathcal{Q} \log \mathcal{Q}) + 2(\mathcal{P} \log 2\mathcal{P} + \mathcal{P}))$.
Using our approximate relationships to $\mathcal{Q}$ given previously and simplifying, we arrive at $O[\mathcal{Q}(2N^2 \log N / \log \mathcal{Q} + (1/N + 4)\log \mathcal{Q} + 2 + log(4))]$.

@@

We gratefully acknowledge support from NIH/NIDA U01DA047638 (EG) and efforts by Dr. Nicole Soranzo to establish a pangenome research unit at the Human Technopole in Milan, Italy (AG).
\linebreak
\linebreak
\textit{Conflict of Interest}: none declared.

>>>>

Considering the time complexity of induction, we anticipate $O(|A|\log|A|)$ time to sort the match set and $O(\mathcal{N} \log |A|)$ to query it and compute our $\mathcal{N}$ transitive closures.
Computing the variation graph paths $\mathcal{P}$ involves converting sequences in $S$ to walks through $\mathcal{N}$.
We first sort the sequence-to-graph mapping array $Z$ in $O(\mathcal{Q} \log \mathcal{Q})$ operations, and then compute $\mathcal{P}$ in $O(\mathcal{Q})$ queries which each cost $O(\log \mathcal{Q})$.
To obtain unique edges and generate $\mathcal{E}$, we must build and sort an array of size $O(2|P|)$, and then iterate through it for $O(2|P| \log 2|P| + 2|P|)$ operations.
In sum, we would expect to require $O(|A|\log|A| + \mathcal{N} \log |A| + 2(\mathcal{Q} \log \mathcal{Q}) + 2(|P| \log 2|P| + |P|))$.
Using our approximate relationships to $\mathcal{Q}$ given previously and simplifying, we arrive at $O[\mathcal{Q}(2N^2 \log N / \log \mathcal{Q} + (1/N + 4)\log \mathcal{Q} + 2 + \log(4))]$.

@@

We gratefully acknowledge support from NIH/NIDA U01DA047638 and NSF PPoSS Award \#2118709 (EG) and efforts by Dr. Nicole Soranzo to establish a pangenome research unit at the Human Technopole in Milan, Italy (AG).
\linebreak
\linebreak
\textit{Conflict of Interest}: none declared.
